The Controlled Choice Design and Paternalism in Pawnshop Borrowing

### 2023-07-04 OA.tex
add loan as predictor in narrow and wide forest

\vspace{.1in}
\begin{table}[H]
        \caption{Effect of Prior Assignment on Subsequent Choice}
    \label{learning_table}
\begin{center}
\scriptsize{\input{./Tables/learning_exp_pres.tex}}
\end{center}
 \scriptsize  This table uses a Linear Probability Model to examine whether randomized treatment assignment on a prior loan taken during the experimental period drives the likelihood of selecting into the commitment product for individuals who go to a branch featuring Choice after the experiment.
\end{table}

@@

\begin{figure}[H]
    \caption{Partition of TuT by behavioral variables.}
    \label{tut_beh_partition}
    \begin{center}
        \centering
        \includegraphics[width=0.55\textwidth]{Figuras/tut_beh_partition.pdf} 
    \end{center}
     \scriptsize  This figure performs a partition of the Treatment on the Untreated, estimating the share of the effect that arises within each of two binary categories.  The top bars examine present bias (individuals are more impatient over one-month time horizon than they are between three and four months).  The bottom bars examine sure confidence (individual reports 100\% probability of repaying at time of taking loan).  Blue bar is the component arising from those without the trait, orange bar from those with the trait. 
      %\footnotesize{ \textit{Do file: }  \texttt{partition_tot_tut.do}
\end{figure}

@@

\vspace{.2in}
\begin{figure}[H]
        \caption{Empirical CDF of Financial Cost: fee-forcing vs status-quo \textcolor{red}{\hl{MAY NEED UPDATING}}}
    \label{ecdf_fc}
    \begin{center}
        \centering
        \includegraphics[width=0.55\textwidth]{Figuras/cdf_fc_pro_2.pdf}
    \end{center}
    \scriptsize This figure plots the empirical cumulative distribution of financial cost. It does this separately for the fee-forcing contract and for the status-quo contract. The doted line at the bottom is the difference of the status-quo CDF minus the fee-forcing CDF. It shows that the CDF of the status quo contract is always below that of the fee-forcing (and this difference is significant for the points indicated by the blue line), and therefore that the former first-order stochastically dominates the later for weakly decreasing utility functions; see Proposition \ref{eq_fosd}.
    % \texttt{ecdf\_fc.do}}
\end{figure}

\begin{figure}[H]
        \caption{Empirical CDF of APR: fee-focing vs status-quo \textcolor{red}{\hl{MAY NEED UPDATING}}}
    \label{ecdf_fc}
    \begin{center}
        \centering
        \includegraphics[width=0.55\textwidth]{Figuras/cdf_eff_pro_2.pdf}
    \end{center}
    \scriptsize This figure plots the empirical cumulative distribution of financial cost. It does this separately for the fee-forcing contract and for the status-quo contract. The doted line at the bottom is the difference of the status-quo CDF minus the fee-forcing CDF. It shows that the CDF of the status quo contract is always below that of the fee-forcing (and this difference is significant for the points indicated by the blue line), and therefore that the former first-order stochastically dominates the later for weakly decreasing utility functions; see Proposition \ref{eq_fosd}.
    % \texttt{ecdf\_eff.do}}
\end{figure}

@@

\todo[inline]{Issac: re-run this exercise with removing the propensity score weights $p(Z)$. Presumably it shouldn't change anything, but it's simpler to explain what we do and probably less noisy

@@

}

@@

This appendix provides formal proofs of the results described in Section \ref{sec:randchoice}, using the notation and assumptions described in Section \ref{sec:potentialOutcomes}. To simplify the presentation, we omit $i$ subscripts throughout this section.
The following assumption collects our exclusion restriction and the key features of our experimental design.

@@

\begin{lem}\mbox{}
\label{lem_randchoice}
   \begin{enumerate}[(i)]
       \item $\mathbbm{E}(D|Z=2) = \mathbb{P}(C=1)$
       \item $\mathbbm{E}(Y|Z=0) = \mathbbm{E}(Y_0)$
       \item $\mathbbm{E}(Y|Z=1) = \mathbbm{E}(Y_1)$
       \item $\mathbbm{E}(Y|D=0,Z=2) = \mathbbm{E}(Y_0|C=0)$
       \item $\mathbbm{E}(Y|D=1,Z=2) = \mathbbm{E}(Y_1|C=1)$
   \end{enumerate} 
\end{lem}

\begin{proof}
Part (i) follows because $Z=2$ implies $D=C$ and $Z$ is independent of $C$.  
Parts (ii) and (iii) follow similarly: given $Z=0$ we have $Y = Y_0$, given $Z=1$ we have $Y = Y_1$, and $Z$ is independent of $(Y_0,Y_1)$.
For parts (iv) and (v), first note that Assumption \ref{assump:randchoice} (iii) implies that $Z$ is conditionally independent of $(Y_0,Y_1)$ given $C$.
Now, $Z=2$ implies that $D=0$ if and only if $C=0$. Hence,
\[
\mathbbm{E}(Y|D=0, Z=2) = \mathbbm{E}(Y_0|D=0, Z=2) = \mathbbm{E}(Y_0|C=0, Z=2)=\mathbbm{E}(Y_0|C=0)
\]
establishing part (iv).
Similarly, $Z=2$ implies that $D=1$ if and only if $C=1$ and hence
\[
\mathbbm{E}(Y|D=1, Z=2) = \mathbbm{E}(Y_1|D=1, Z=2) = \mathbbm{E}(Y_1|C=1, Z=2)= \mathbbm{E}(Y_1|C=1)
\]
establishing part (v).
\end{proof}

\begin{prop} \mbox{}
    \begin{enumerate}[(i)]
        \item $\text{ToT} \equiv \mathbbm{E}(Y_1 - Y_0|C=1)  = \displaystyle \frac{\mathbbm{E}(Y|Z=2) - \mathbbm{E}(Y|Z=0)}{\mathbbm{E}(D|Z=2)}$
        \item $\text{TuT} \equiv \mathbbm{E}(Y_1 - Y_0|C=0) = \displaystyle \frac{\mathbbm{E}(Y|Z=1) - \mathbbm{E}(Y|Z=2)}{1 - \mathbbm{E}(D|Z=2)}$
        \item $\text{ASB} \equiv \mathbbm{E}(Y_0|C=1) - \mathbbm{E}(Y_0|C=0) = \displaystyle \frac{\mathbbm{E}(Y|Z=0) - \mathbbm{E}(Y|Z=2,D=0)}{\mathbbm{E}(D|Z=2)}$
        \item $\text{ASL} \equiv \mathbbm{E}(Y_1|C=1) - \mathbbm{E}(Y_1|C=0) = \displaystyle \frac{\mathbbm{E}(Y|Z=2,D=1) - \mathbbm{E}(Y|Z=1)}{1 - \mathbbm{E}(D|Z=2)}$
    \end{enumerate}
\end{prop}

\begin{proof}
For parts (i) and (iii) we require an expression for $\mathbbm{E}(Y_0|C=1)$ in terms of the observables $(Y, D, Z)$.
By Lemma \ref{lem_randchoice}(ii) and iterated expectations 
\[
\mathbbm{E}(Y|Z=0) = \mathbbm{E}(Y_0) = \mathbbm{E}(Y_0|C=0) \mathbbm{P}(C=0) + \mathbbm{E}(Y_0|C=1) \mathbbm{P}(C=1).
\]
Re-arranging and substituting Lemma \ref{lem_randchoice}(i) and (iv),
\begin{equation}
\mathbbm{E}(Y_0|C=1)  = \frac{\mathbbm{E}(Y|Z=0) - \mathbbm{E}(Y_0|C=0) \mathbbm{P}(C=0)}{\mathbbm{P}(C=1)} =  \frac{\mathbbm{E}(Y|Z=0) - \mathbbm{E}(Y|Z=2,D=0) \mathbbm{E}(1 - D|Z=2)}{\mathbbm{E}(D|Z=2)}.
\label{eq:Y0C1}
\end{equation}
Part (i) follows by combining \eqref{eq:Y0C1} with Lemma \ref{lem_randchoice}(v) and simplifying; part (iii) follows by combining \eqref{eq:Y0C1} with Lemma \ref{lem_randchoice}(iv) and simplifying.
Similarly, for parts (ii) and (iv) we require an expression for $\mathbbm{E}(Y_1|C=0)$ in terms of observables.
By Lemma \ref{lem_randchoice}(iii) and iterated expectations,
\[
\mathbbm{E}(Y|Z=1) = \mathbbm{E}(Y_1) = \mathbbm{E}(Y_1|C=0)\mathbbm{P}(C=0) + \mathbbm{E}(Y_1|C=1) \mathbbm{P}(C=1).
\]
Re-arranging and substituting Lemma \ref{lem_randchoice}(i) and (v),
\begin{equation}
\mathbbm{E}(Y_1|C=0) 
= \frac{\mathbbm{E}(Y|Z=1) - \mathbbm{E}(Y_1|C=1)\mathbbm{P}(C=1)}{\mathbb{P}(D=0)} =\frac{\mathbbm{E}(Y|Z=1) - \mathbbm{E}(Y|Z=2,D=1)\mathbbm{E}(D|Z=2)}{\mathbb{E}(1-D|Z=2)}.
\label{eq:Y1C0}
\end{equation}
Part (ii) follows by combining \eqref{eq:Y1C0} with Lemma \ref{lem_randchoice}(iv) and simplifying; part (iv) follows by combining \eqref{eq:Y1C0} with Lemma \ref{lem_randchoice}(v) and simplifying.
\end{proof}

\todo[inline]{It looks like I still need to paste in the derivations of the ``regression'' approach to identifying the effects of interest. I will do this pronto! -Frank}

@@

\section{LATE: ToT \& TuT}
\vspace{.2in}
\normalsize
\linespread{1.25}
%Really force it to normal size and linespread
\normalsize
\linespread{1.25}

>>>>

\vspace{.1in}
\begin{table}[H]
        \caption{Effect of Prior Assignment on Subsequent Choice}
    \label{learning_table}
\begin{center}
\scriptsize{\input{./Tables/learning_exp.tex}}
\end{center}
 \scriptsize  This table uses a Linear Probability Model to examine whether randomized treatment assignment on a prior loan taken during the experimental period drives the likelihood of selecting into the commitment product for individuals who go to a branch featuring Choice after the experiment.
\end{table}

@@

\begin{figure}[H]
    \caption{Partition of TUT by behavioral variables.}
    \label{tut_beh_partition}
    \begin{center}
        \centering
        \includegraphics[width=0.55\textwidth]{Figuras/tut_beh_partition.pdf} 
    \end{center}
     \scriptsize  This figure performs a partition of the Treatment on the Untreated (FC), estimating the share of the effect that arises within each of two binary categories.  The top bars examine present bias (individuals are more impatient over one-month time horizon than they are between three and four months).  The bottom bars examine sure confidence (individual reports 100\% probability of repaying at time of taking loan).  Blue bar is the component arising from those without the trait, orange bar from those with the trait. 
      %\footnotesize{ \textit{Do file: }  \texttt{partition_tot_tut.do}
\end{figure}

@@

\vspace{.2in}
\begin{figure}[H]
        \caption{Empirical CDF of Financial Cost: Forced commitment vs Control }
    \label{ecdf_fc}

    \begin{center}
       \begin{subfigure}{0.49\textwidth}
        \caption{APR}
        \centering
        \includegraphics[width=\textwidth]{Figuras/cdf_apr.pdf}
    \end{subfigure} 
   \begin{subfigure}{0.49\textwidth}
        \caption{Financial cost}
        \centering
        \includegraphics[width=\textwidth]{Figuras/cdf_fc_admin.pdf}
    \end{subfigure} 
    \end{center}
    \scriptsize This figure plots the empirical cumulative distribution of financial cost. It does this separately for the fee-forcing contract and for the status-quo contract. The dotted line at the bottom is the difference of the control CDF minus the forced CDF arm. It shows that the CDF of the status quo contract is always below that of the fee-forcing (and this difference is significant for the points indicated by the blue line), and therefore that the former first-order stochastically dominates the later for weakly decreasing utility functions; see Proposition \ref{eq_fosd}.
    % \texttt{fosd_ecdf.do}}
\end{figure}

@@

\todo[inline]{Issac: re-run this exercise with removing the propensity score weights $p(Z)$. Presumably it shouldn't change anything, but it's simpler to explain what we do and probably less noisy}

@@

@@

This appendix provides proofs of the results described in Section \ref{sec:randchoice}, using the notation and assumptions described in Section \ref{sec:potentialOutcomes}. 
To simplify the presentation, we omit $i$ subscripts throughout this section.
We also use the shorthand $Z_0 \equiv \mathbbm{1}(Z=0)$, $Z_1 \equiv \mathbbm{1}(Z=1)$, and $Z_2 \equiv\mathbbm{1}(Z=2)$.
For convenience, the following assumption collects our exclusion restriction and the key features of the constrained choice design.

@@

\subsection{Point Identification}

We first show that the TOT, TUT, ASB, and ASL effects are point identified under the constrained choice design.
It follows that the ASG effect, $(\text{TOT} - \text{TUT})$, is likewise point identified.

\begin{lem}
Under Assumption \ref{assump:randchoice},
\label{lem_randchoice}
   \begin{enumerate}[(i)]
       \item $\mathbbm{E}(D|Z=2) = \mathbb{P}(C=1)$
       \item $\mathbbm{E}(Y|Z=0) = \mathbbm{E}(Y_0)$
       \item $\mathbbm{E}(Y|Z=1) = \mathbbm{E}(Y_1)$
       \item $\mathbbm{E}(Y|D=0,Z=2) = \mathbbm{E}(Y_0|C=0)$
       \item $\mathbbm{E}(Y|D=1,Z=2) = \mathbbm{E}(Y_1|C=1)$.
   \end{enumerate} 
\end{lem}

\begin{proof}
Part (i) follows because $Z=2$ implies $D=C$ and $Z$ is independent of $C$.  
Parts (ii) and (iii) follow similarly: given $Z=0$ we have $Y = Y_0$, given $Z=1$ we have $Y = Y_1$, and $Z$ is independent of $(Y_0,Y_1)$.
For parts (iv) and (v), first note that Assumption \ref{assump:randchoice} (iii) implies that $Z$ is conditionally independent of $(Y_0,Y_1)$ given $C$.
Now, $Z=2$ implies that $D=0$ if and only if $C=0$. Hence,
\[
\mathbbm{E}(Y|D=0, Z=2) = \mathbbm{E}(Y_0|D=0, Z=2) = \mathbbm{E}(Y_0|C=0, Z=2)=\mathbbm{E}(Y_0|C=0)
\]
establishing part (iv).
For part (v) $Z=2$ implies that $D=1$ if and only if $C=1$ and hence
\[
\mathbbm{E}(Y|D=1, Z=2) = \mathbbm{E}(Y_1|D=1, Z=2) = \mathbbm{E}(Y_1|C=1, Z=2)= \mathbbm{E}(Y_1|C=1). %\qedhere
\]
\end{proof}

\begin{prop} 
Under Assumption \ref{assump:randchoice},
    \begin{enumerate}[(i)]
        \item $\text{TOT} \equiv \mathbbm{E}(Y_1 - Y_0|C=1)  = \displaystyle \frac{\mathbbm{E}(Y|Z=2) - \mathbbm{E}(Y|Z=0)}{\mathbbm{E}(D|Z=2)}$
        \item $\text{TUT} \equiv \mathbbm{E}(Y_1 - Y_0|C=0) = \displaystyle \frac{\mathbbm{E}(Y|Z=1) - \mathbbm{E}(Y|Z=2)}{1 - \mathbbm{E}(D|Z=2)}$
        \item $\text{ASB} \equiv \mathbbm{E}(Y_0|C=1) - \mathbbm{E}(Y_0|C=0) = \displaystyle \frac{\mathbbm{E}(Y|Z=0) - \mathbbm{E}(Y|Z=2,D=0)}{\mathbbm{E}(D|Z=2)}$
        \item $\text{ASL} \equiv \mathbbm{E}(Y_1|C=1) - \mathbbm{E}(Y_1|C=0) = \displaystyle \frac{\mathbbm{E}(Y|Z=2,D=1) - \mathbbm{E}(Y|Z=1)}{1 - \mathbbm{E}(D|Z=2)}$.
    \end{enumerate}
\end{prop}

\begin{proof}
For parts (i) and (iii) we require an expression for $\mathbbm{E}(Y_0|C=1)$ in terms of the observables $(Y, D, Z)$.
By Lemma \ref{lem_randchoice}(ii) and iterated expectations 
\[
\mathbbm{E}(Y|Z=0) = \mathbbm{E}(Y_0) = \mathbbm{E}(Y_0|C=0) \mathbbm{P}(C=0) + \mathbbm{E}(Y_0|C=1) \mathbbm{P}(C=1).
\]
Re-arranging and substituting Lemma \ref{lem_randchoice}(i) and (iv),
\begin{align}
\mathbbm{E}(Y_0|C=1)  &= \frac{\mathbbm{E}(Y|Z=0) - \mathbbm{E}(Y_0|C=0) \mathbbm{P}(C=0)}{\mathbbm{P}(C=1)}\nonumber\\ 
&=  \frac{\mathbbm{E}(Y|Z=0) - \mathbbm{E}(Y|Z=2,D=0) \mathbbm{E}(1 - D|Z=2)}{\mathbbm{E}(D|Z=2)}.
\label{eq:Y0C1}
\end{align}
Part (i) follows by combining \eqref{eq:Y0C1} with Lemma \ref{lem_randchoice}(v) and simplifying; part (iii) follows by combining \eqref{eq:Y0C1} with Lemma \ref{lem_randchoice}(iv) and simplifying.
Similarly, for parts (ii) and (iv) we require an expression for $\mathbbm{E}(Y_1|C=0)$ in terms of observables.
By Lemma \ref{lem_randchoice}(iii) and iterated expectations,
\[
\mathbbm{E}(Y|Z=1) = \mathbbm{E}(Y_1) = \mathbbm{E}(Y_1|C=0)\mathbbm{P}(C=0) + \mathbbm{E}(Y_1|C=1) \mathbbm{P}(C=1).
\]
Re-arranging and substituting Lemma \ref{lem_randchoice}(i) and (v),
\begin{align}
\mathbbm{E}(Y_1|C=0) 
&= \frac{\mathbbm{E}(Y|Z=1) - \mathbbm{E}(Y_1|C=1)\mathbbm{P}(C=1)}{\mathbb{P}(D=0)} \nonumber\\
&=\frac{\mathbbm{E}(Y|Z=1) - \mathbbm{E}(Y|Z=2,D=1)\mathbbm{E}(D|Z=2)}{\mathbb{E}(1-D|Z=2)}.
\label{eq:Y1C0}
\end{align}
Part (ii) follows by combining \eqref{eq:Y1C0} with Lemma \ref{lem_randchoice}(iv) and simplifying; part (iv) follows by combining \eqref{eq:Y1C0} with Lemma \ref{lem_randchoice}(v) and simplifying.
\end{proof}

\subsection{Regression-based Estimation of TOT, TUT, ASG, ASL, and ASB}

We now show how a collection of just-identified, linear IV regressions can be used to consistently estimate the ATE, TOT, and TUT effects, along with each of the ingredients needed to construct the ASL and ASB. 
These results are used below to provide a recipe for cluster-robust inference for the ASG, ASL, and ASB effects.
The first result provides a regression-based approach to estimate the ATE and TOT.

\begin{prop} 
Under Assumption \ref{assump:randchoice},
\[
Y = \mathbbm{E}(Y_0) + \text{ATE}\times Z_1 + \text{TOT} \times Z_2 D + U
\]
where $\mathbb{E}(U|Z) = 0$.
Therefore, under standard regularity conditions, an IV regression of $Y$ on an intercept, $Z_1$ and $Z_2 D$ with instruments $(1, Z_1, Z_2)$ provides a consistent estimator of the ATE and TOT effects.
\end{prop}

\begin{proof}
By Assumption \ref{assump:randchoice} (iii),
\begin{align*}
Y &= Z_0 Y_0 + Z_1 Y_1 + Z_2[(1 - C) Y_0 + CY_1]\\
&= (Z_0 + Z_2)Y_0 + Z_1 Y_1 + Z_2C(Y_1 - Y_0)\\
&= (Z_0 + Z_1 + Z_2)Y_0 + Z_1 (Y_1 - Y_0) + Z_2D(Y_1 - Y_0)\\
&= Y_0 + Z_1 (Y_1 - Y_0) + Z_2D(Y_1 - Y_0).
\end{align*}
since $Z_2 D = Z_2 C$ and $(Z_0 + Z_1 + Z_2) = 1$.
Thus, defining 
\[
U \equiv [Y_0 - \mathbbm{E}(Y_0)] + Z_1[(Y_1 - Y_0) - \text{ATE}] + Z_2 D[(Y_1 - Y_0) - \text{TOT}]
\]
by construction we have
\[
Y = \mathbbm{E}(Y_0) + \text{ATE} \times Z_1 + \text{TOT} \times Z_2 D+ U.
\]
Now, since $Z_2 D = Z_2 C$ and $Z$ is independent of $(Y_1, Y_0)$ by Assumption \ref{assump:randchoice} (i), we have
\begin{align*}
\mathbbm{E}(U|Z) &= [\mathbbm{E}(Y_0|Z) - \mathbbm{E}(Y_0)]  + Z_1[\mathbbm{E}(Y_1 - Y_0|Z) - \text{ATE}] +  \mathbbm{E}\left[Z_2 D\left\{(Y_1 - Y_0) - \text{TOT}\right\}|Z\right]\\
&= [\mathbbm{E}(Y_0) - \mathbbm{E}(Y_0)]  + Z_1[\mathbbm{E}(Y_1 - Y_0) - \text{ATE}] + Z_2 \mathbbm{E}\left[C\left\{(Y_1 - Y_0) - \text{TOT}\right\}|Z\right]\\
&= Z_2 \mathbbm{E}\left[C\left\{(Y_1 - Y_0) - \text{TOT}\right\}|Z\right].
\end{align*}
Finally, by iterated expectations
\begin{align*}
\mathbbm{E}\left[C\left\{(Y_1 - Y_0) - \text{TOT}\right\}|Z\right] &=  \mathbbm{P}(C=1|Z) \left[\mathbbm{E}(Y_1 - Y_0|C=1,Z)  - \text{TOT}\right]\\
&= \mathbbm{P}(C=1)\left[\mathbbm{E}(Y_1 - Y_0|C=1) - \text{TOT} \right]=0
\end{align*}
since $Z$ is conditionally independent of $(Y_0, Y_1)$ given $C$, an implication of \ref{assump:randchoice} (i).
\end{proof}

The next proposition provides regression-based estimates of the ATE and TUT.
\begin{prop}
Under Assumption \ref{assump:randchoice}
\[
Y = \mathbbm{E}(Y_1) + \text{ATE}\times -Z_0 + \text{TUT} \times -Z_2 (1 - D) + V
\] 
where $\mathbb{E}(V|Z) = 0$.
Therefore, under standard regularity conditions, an IV regression of $Y$ on an intercept, $-Z_0$ and $-Z_2(1-D)$ with instruments $(1, Z_0, Z_2)$ provides consistent estimates of the ATE and TUT effects.
\end{prop}

\begin{proof}
By Assumption \ref{assump:randchoice} (iii),
\begin{align*}
Y &= Z_0 Y_0 + Z_1 Y_1 + Z_2[(1 - C) Y_0 + CY_1]\\
&= Z_0 Y_0 + Z_1 Y_1 + Z_2[(1 - C) (Y_0 - Y_1) + Y_1]\\
&= Z_0 Y_0 + (Z_1 + Z_2) Y_1 + Z_2(1 - C) (Y_0 - Y_1) \\
&= Z_0 Y_0 + (1 - Z_0) Y_1 + Z_2(1 - D) (Y_0 - Y_1) \\
&= Y_1 - Z_0 (Y_1 - Y_0) - Z_2(1 - D) (Y_1 - Y_0)
\end{align*}
since $Z_2(1 - C)= Z_2(1 - D)$ and $(Z_1 + Z_2) = 1 - Z_0$.
Thus, defining 
\[
V \equiv [Y_1 - \mathbb{E}(Y_1)] - Z_0[(Y_1 - Y_0) - \text{ATE}] - Z_2(1 - D)[(Y_1 - Y_0) - \text{TUT}]
\]
by construction we have
\[
Y = \mathbb{E}(Y_1) + \text{ATE} \times -Z_0 + \text{TUT} \times -Z_2(1 - D) + V.
\]
Now, since $Z_2(1 - D) = Z_2 (1 - C)$ and $Z$ is independent of $(Y_0, Y_1)$ by Assumption \ref{assump:randchoice} (i),
\begin{align*}
\mathbb{E}(V|Z) &= [\mathbb{E}(Y_1|Z) - \mathbb{E}(Y_1)] - Z_0[\mathbb{E}(Y_1 - Y_0|Z) - \text{ATE}] - \mathbb{E}[Z_2(1 - D)\left\{(Y_1 - Y_0) - \text{TUT}\right\}|Z]\\
&= [\mathbb{E}(Y_1) - \mathbb{E}(Y_1)] - Z_0[\mathbb{E}(Y_1 - Y_0) - \text{ATE}] - Z_2\mathbb{E}[(1 - C)\left\{(Y_1 - Y_0) - \text{TUT}\right\}|Z]\\
&= -Z_2\mathbb{E}[(1 - C)\left\{(Y_1 - Y_0) - \text{TUT}\right\}|Z].
\end{align*}
Finally, by iterated expectations,
\begin{align*}
\mathbb{E}[(1 - C)\left\{(Y_1 - Y_0) - \text{TUT}\right\}|Z]&= \mathbb{P}(C=0|Z)\left[ \mathbb{E}(Y_1 - Y_0|C=0, Z) - \text{TUT}\right]\\
&= \mathbb{P}(C=0|Z) \left[ \mathbb{E}(Y_1 - Y_0|C=0) - \text{TUT}\right] = 0
\end{align*}
since $Z$ is conditionally independent of $(Y_0, Y_1)$ given $C$, an implication of Assumption \ref{assump:randchoice} (i).
\end{proof}

Since $\text{ASG} = \text{TOT} - \text{TUT}$, the preceding two propositions provide consistent estimates of $\text{ASG}$ effect.
The $\text{ASB}$ effect, $\mathbbm{E}(Y_0|C=1) - \mathbb{E}(Y_0|C=0)$, can likewise be estimated by taking the difference of coefficients across two linear IV regressions, as shown in the following proposition.

\begin{prop}
Under Assumption \ref{assump:randchoice}
\begin{align}
\label{eq:ASB0}
    (1 - D) Y &= \mathbbm{E}(Y_{0}) \times Z_0 + \mathbbm{E}(Y_{0}|C=0) \times (1 - D)Z_2 + U_{0}\\
\label{eq:ASB1}
    (1 - D) Y &= \mathbbm{E}(Y_{0}) \times(Z_0 + Z_2) + \mathbbm{E}(Y_{0}|C=1)\times -DZ_2 + U_{1}
\end{align}
where $\mathbbm{E}(U_0|Z) = \mathbbm{E}(U_1|Z) = 0$.
Thus, under standard regularity conditions, an IV regression of $(1 - D)Y$ on $Z_0$ and $(1 - D)Z_2$ with instruments $(Z_0, Z_2)$ and no intercept provides consistent estimates of $\mathbb{E}(Y_0)$ and $\mathbb{E}(Y_0|C=0)$. 
Similarly, an IV regression of $(1 - D)Y$ on $(Z_0 + Z_2)$ and $-DZ_2$ with instruments $(Z_0, Z_2)$ and no intercept provides consistent estimates of $\mathbb{E}(Y_0)$ and $\mathbb{E}(Y_0|C=1)$.
\end{prop}

\begin{proof}
Assumption \ref{assump:randchoice} (ii) implies $(1 - D) = Z_0 + Z_2(1 - C)$. Hence, by Assumption \ref{assump:randchoice} (iii),
\begin{align*}
(1 - D)Y &=  [Z_0 + Z_2 (1 - C)]\left\{Z_0 Y_0 + Z_1 Y_1 + Z_2[(1 - C) Y_0 + CY_1]\right\}\\
&= Z_0 Y_0 + Z_2 (1 - C) [(1 - C) Y_0 + C Y_1]\\
&= Z_0 Y_0 + Z_2 (1 - C) Y_0.
\end{align*}
because $Z_j^2 = Z_j$ for any $j$ and $Z_j Z_k = 0$ for any $j \neq k$ and, similarly, $(1 - C)^2 = (1 - C)$ and $C (1 - C) = 0$.
Therefore, since $Z_2 (1 - C) = Z_2 (1 - D)$,
\begin{align*}
(1 - D)Y &= Z_0 Y_0 + Z_2 (1 - D) Y_0\\
(1 - D)Y &= (Z_0 + Z_2) Y_0 + (-DZ_2) Y_0. 
\end{align*}
Now, defining
\begin{align*}
U_0 &\equiv Z_0 [Y_0 - \mathbbm{E}(Y_0)] + Z_2(1 - D)[Y_0 - \mathbbm{E}(Y_0|C=0)]\\
U_1 &\equiv (Z_0 + Z_2)[Y_0 - \mathbbm{E}(Y_0)] + (-Z_2 D)[Y_0 - \mathbbm{E}(Y_0|C=1)]
\end{align*}
by construction, we have
\begin{align*}
Y &= \mathbbm{E}(Y_0) \times Z_0 + \mathbbm{E}(Y_0|C=0) \times Z_2(1 - D) + U_0\\
Y &= \mathbbm{E}(Y_0) \times (Z_0 + Z_2)+ \mathbbm{E}(Y_0|C=1) (-Z_2D) + U_1.
\end{align*}
Finally, since $Z_2(1-D) = Z_2(1 - C)$, and $Z$ is independent of $Y_0$,  
\begin{align*}
\mathbbm{E}(U_0|Z) &= Z_0[\mathbbm{E}(Y_0|Z) - \mathbbm{E}(Y_0)] + Z_2\mathbbm{E}\{(1 - C) [Y_0 - \mathbbm{E}(Y_0|C=0) |Z\}\\
&= Z_2 \mathbbm{E}[Y_0 - \mathbbm{E}(Y_0|C=0) | C = 0, Z] = 0
\end{align*}
where the final two steps follow by iterated expectations and the fact that  $Z$ is conditionally independent of $Y_0$ given $C$. 
Since $Z_2 D = Z_2 C$, a nearly identical argument gives
\begin{align*}
\mathbbm{E}(U_1|Z) &= (Z_0 + Z_2)[Y_0 - \mathbbm{E}(Y_0|Z)] -Z_2\mathbbm{E}\{C [Y_0 - \mathbbm{E}(Y_0|C=1) |Z\}\\
&= -Z_2 \mathbbm{E}[Y_0 - \mathbbm{E}(Y_0|C=0) | C = 1, Z] = 0. \qedhere
\end{align*}
\end{proof}

The next results shows that the $\text{ASL}$ effect, $\mathbbm{E}(Y_1|C=1) - \mathbb{E}(Y_1|C=0)$, can be estimated as the difference of coefficients across two linear IV regressions, as shown in the following proposition.

\begin{prop}
Under Assumption \ref{assump:randchoice},
\begin{align}
\label{eq:ASL0}
    D Y &= \mathbbm{E}(Y_{1}) \times(Z_1 + Z_2) + \mathbbm{E}(Y_{1}|C=0)\times (D - 1)Z_2 + V_{0}\\
\label{eq:ASL1}
    D Y &= \mathbbm{E}(Y_{1}) \times Z_1 + \mathbbm{E}(Y_{1}|C=1)\times D Z_2+ V_{1}
\end{align}
where $\mathbbm{E}(V_0|Z) = \mathbbm{E}(V_1|Z) = 0$.
Thus, under standard regularity conditions, an IV regression of $DY$ on $(Z_1 + Z_2)$ and $-Z_2(1 - D)$ with instruments $(Z_1, Z_2)$ and no intercept provides consistent estimates of $\mathbb{E}(Y_1)$ and $\mathbb{E}(Y_1|C=1)$.
Similarly, an IV regression of $DY$ on $Z_1$ and $DZ_2$ with instruments $(Z_1, Z_2)$ and no intercept provides consistent estimates of $\mathbb{E}(Y_1)$ and $\mathbb{E}(Y_1|C=1)$. 
\end{prop}

\begin{proof}
By Assumption \ref{assump:randchoice}, $D = Z_1 + Z_2 C$. Hence, by Assumption \ref{assump:randchoice} (iii),
\begin{align*}
DY &=  (Z_1 + Z_2 C)\left\{Z_0 Y_0 + Z_1 Y_1 + Z_2[(1 - C) Y_0 + CY_1]\right\}\\
&= Z_1 Y_1 + Z_2 C[(1 -C) Y_0 + C Y_1]\\
&= Z_1 Y_1 + Z_2 C Y_1
\end{align*}
because $Z_j^2 = Z_j$ for any $j$ and $Z_j Z_k = 0$ for any $j \neq k$ and, similarly, $(1 - C)^2 = (1 - C)$ and $C (1 - C) = 0$. Therefore, since $Z_2 (1 - C) = Z_2 (1 - D)$,
\begin{align*}
 DY &= (Z_1 + Z_2)Y_1 + Z_2 (D - 1) Y_1\\
 DY &= Z_1 Y_1 + Z_2 D Y_1.
\end{align*}
Now, defining
\begin{align*}
V_0 &= (Z_1 + Z_2)[Y_1 - \mathbbm{E}(Y_1)] + Z_2(D - 1)[Y_1 - \mathbbm{E}(Y_1|C=0)]\\
V_1 &= Z_1[Y_1 - \mathbbm{E}(Y_1)] + Z_2D[Y_1 - \mathbbm{E}(Y_1|C=1)]
\end{align*}
by construction we have
\begin{align*}
Y &= \mathbbm{E}(Y_1) \times (Z_1 + Z_2) + \mathbbm{E}(Y_1 | C = 0) \times Z_2 (D - 1) + V_0\\
Y &= \mathbbm{E}(Y_1) \times Z_1 + \mathbbm{E}(Y_1 | C = 1) \times Z_2 D + V _1.
\end{align*}
Finally, since $Z_2(1 - D) = Z_2(1 - C)$ and $Z$ is independent of $Y_1$,
\begin{align*}
\mathbbm{E}(V_0|Z) &= (Z_1 + Z_2) [\mathbbm{E}(Y_1|Z) - \mathbbm{E}(Y_1) ]  - Z_2 \mathbbm{E}\{(1 - C)  [Y_1 - \mathbbm{E}(Y_1 | C=0)|Z\} \\
&= -Z_2 \mathbbm{E}[Y_1 - \mathbbm{E}(Y_1 | C=0)|C=0, Z] = 0
\end{align*}
where the final two steps follow by iterated expectations and the fact that  $Z$ is conditionally independent of $Y_1$ given $C$. 
Since $Z_2 D = Z_2 C$, a nearly identical argument gives
\begin{align*}
\mathbbm{E}(V_1|Z) &= Z_1 [\mathbbm{E}(Y_1 | Z) - \mathbbm{E}(Y_1)]  + Z_2 \mathbbm{E}\{C  [Y_1 - \mathbbm{E}(Y_1 | C=1)|Z\} \\
&= Z_2 \mathbbm{E}[Y_1 - \mathbbm{E}(Y_1 | C=1)|C=1, Z] = 0. \qedhere
\end{align*}
\end{proof}

\todo[inline]{Update below here}

\subsection{Inference for ASG, ASB, and ASL}
We now explain how to carry out cluster-robust inference for the ASG, ASB, and ASL effects, as implemented in our companion STATA package.

For purposes of inference, both the ASB and ASL can be re-written as the difference of coefficients from a pair of just-identified linear IV regressions, namely

As in the case of the ASG, inference for the ASB and ASL can be carried out by saving the residuals from \eqref{eq:ASB0}--\eqref{eq:ASL1}.

\todo[inline]{Add something about the TUT decomposition and covariates? Probably just a few sentences at most.}

@@

%\section{LATE: TOT \& TUT}
%\vspace{.2in}
%\normalsize
%\linespread{1.25}
%%Really force it to normal size and linespread
%\normalsize
%\linespread{1.25}
%
